### 2022-01-20 src-latex/parts/10-introduction.tex
Shrink abstract and put fig in 1st page

% !TeX root = ../main-paper.tex
\section{Introduction}

\textbf{TODO sample (simplified) pipeline of the information extraction process}
\textbf{and/or}
\textbf{TODO illustration a sample page (full image, large crop, entry crop with highlighted entities)}

>>>>

% !TeX root = ../main-paper.tex
\begin{figure}[!h]
    \centering
    \includegraphics[width=.9\textwidth]{figs/overview-intro.pdf}
    \caption{%
    Overview of the pipeline under study.
    From previously-extracted images of directory entries, 
    we perform OCR and named entity recognition (NER) using different techniques.
    We aim at answering the following questions:
    \emph{How noisy are modern, out-of-the-box OCR systems?}
    \emph{What is the behavior of NER when OCR is noisy?}
    \emph{Can NER be made more robust to OCR noise?}
    }
    \label{<label>}
\end{figure}
\clearpage% force float flush!

\section{Introduction}
